### 2019-12-20 report/02-methods.Rmd
Compute sensibility

# Add alt, lat, etc...
habitat_station %<>% 
  left_join(geo_station, by = "station") %>%
  select(-region_csp)
# Add temp and flow
flow_temp <- temporal_press_polluants %>%
  filter(category %in% c("flow", "temperature", "DBO", "herbicides",
      "fungicides", "insecticides", "nitrates", "phosphore")) %>%
  rename(station = id) 
flow_temp_med <- flow_temp %>%
  mutate(category = str_c(category, "_med")) %>%
  select(station, category, press_med) %>%
  spread(category, press_med)
flow_temp_cv <- flow_temp %>%
  mutate(category = str_c(category, "_cv")) %>%
  select(station, category, cv_press) %>%
  spread(category, cv_press)

>>>>

# Add alt, lat, etc...
habitat_station %<>% 
  left_join(geo_station, by = "station") %>%
  select(-region_csp)

# Add temp and flow
flow_temp <- temporal_press_polluants %>%
  filter(category %in% c("flow", "temperature", "DBO", "herbicides",
      "fungicides", "insecticides", "nitrates", "phosphore")) %>%
  rename(station = id) 
flow_temp_med <- flow_temp %>%
  mutate(category = str_c(category, "_med")) %>%
  select(station, category, press_med) %>%
  spread(category, press_med)
flow_temp_cv <- flow_temp %>%
  mutate(category = str_c(category, "_cv")) %>%
  select(station, category, cv_press) %>%
  spread(category, cv_press)

### 2019-12-20 report/05-stability.Rmd
Compute sensibility

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
myload(network_analysis, dir = mypath("data", "classes"))
myload( trophic_level, trophic_class, dir = mypath("data"))
myload(hab_type, dir = mypath("report"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "local_network_build.R"))
stab_div_troph <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) 
```

@@

```{r}
myload(nmds, dir = mypath("report"))

@@

```{r}
mod <- lm(betadiv_bin ~ log(richness_med), data = temporal_community_metrics)
temporal_community_metrics$beta_bin_c <- resid(mod)
```

```{r}
biomass_sem <- temporal_community_metrics %>%
  select(station, biomass_stab, biomass_med, richness_med, pielou_med,
  beta_bin_c) %>%
  left_join(select(synchrony, station, synchrony, cv_sp), by = "station") %>%
  rename(sync = synchrony,
    piel = pielou_med,
    prod = biomass_med 
  )
habitat_sem <- habitat_pressure %>% 
  select(station, lat, alt, width_river_mean, DBO_med, DBO_cv, flow_med, flow_cv,
    temperature_med, temperature_cv) %>%
  rename(width = width_river_mean)
net_sem <- temporal_network_metrics %>%
  select(station, connectance_corrected_med, w_trph_lvl_avg_med) %>%
  rename(c_c = connectance_corrected_med,
    t_lvl = w_trph_lvl_avg_med)
composition_axis <- nmds$points %>%
  as_tibble %>%
  mutate(station = as.integer(dimnames(nmds$points)[[1]]))

dsem <- biomass_sem  %>%
  mutate(log_rich = log10(richness_med)) %>%
  left_join(net_sem, by = "station") %>%
  left_join(habitat_sem, by = "station") %>%
  left_join(st_basin, by = "station") %>%
  #left_join(composition_axis, by = "station") %>%
  na.omit()

lav_data <- dsem %>%
  mutate(
    log_sync = log10(sync), 
    log_cv_sp = log10(cv_sp),
    log_stab = log10(biomass_stab)
  )
```

```{r, eval = FALSE}
library(lavaan)
options(width = 100)

#log_stab ~ log_sync + log_cv_sp
lav_formula <- "
  log_sync ~ log_rich + piel + alt + c_c + t_lvl + beta_bin_c
  log_cv_sp ~ log_rich + piel + c_c + t_lvl + beta_bin_c
  log_rich ~ alt + width 
  piel ~ alt + width
  c_c ~ alt + width
  t_lvl ~ alt + width
  beta_bin_c ~ alt + width
  log_cv_sp ~~ log_sync
  "
lav_mod <- sem(lav_formula, lav_data)

standardizedsolution(lav_mod) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```

```{r, eval = FALSE, fig.dim = c(10, 7), fig.cap = "Lavaan SEM"}
ggsem(lav_mod)
```

@@

```{r, fig.cap = "The basic SEM"}
build_stab_sem <- function (evt = NULL, com = NULL, stab_comp = NULL, stab = NULL,  .data = NULL) {

@@

source(mypath("R", "plot_methods.R"))
ggpiecewisesem(output)
```
```{r}

@@

```{r}
compute_psem <- function(.data) {
  corsem <- psem(
    lme(temperature_med ~ alt, random = ~ 1 | basin, data = .data),
    lme(log_rich ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
    lme(piel ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
    lme(c_c ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
    lme(t_lvl ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
    lme(beta_bin_c ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
    lme(log_sync ~ log_rich + piel + alt + c_c + t_lvl + beta_bin_c,
      random = ~ 1 | basin, data = .data),
    lme(log_cv_sp ~ log_rich + piel + c_c + t_lvl +
    beta_bin_c, random = ~ 1 | basin, data = .data),
    lm(log_stab ~ log_cv_sp + log_sync, data = .data)
  )
  output <- summary(corsem, .progressBar = F)

  output
}
test <- compute_psem(lav_data)
ggpiecewisesem(test)
```

@@

```{r sensitivity, eval = FALSE}
myload(op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))

# Compute stability, network metrics, etc with the new datasets

# Compute SEMs
map(list(), compute_psem)

# Plot

>>>>

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
myload(network_analysis, dir = mypath("data", "classes"))
myload( trophic_level, trophic_class, dir = mypath("data"))
myload(hab_type, habitat_pressure, dir = mypath("report"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "local_network_build.R"))
stab_div_troph <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) 
```

@@

@@

```{r}
myload(nmds, dir = mypath("report"))
lav_data <- compute_sem_dataset(
  com = temporal_community_metrics,
  network = temporal_network_metrics, 
  hab_press = habitat_pressure, 
  sync = synchrony,
  nmds = nmds,
  basin = st_basin 
  )
```

@@

```{r, eval = FALSE, fig.cap = "The basic SEM"}
build_stab_sem <- function (evt = NULL, com = NULL, stab_comp = NULL, stab = NULL,  .data = NULL) {

@@

source(mypath("R", "plot_methods.R"))
ggpiecewisesem(output)
```
```{r, eval = FALSE}

@@

```{r}
library(nlme)
library(piecewiseSEM)

st_basin <- get_basin_station()
myload(nmds, dir = mypath("report"))

# Compute stability, network metrics, etc with the new datasets
com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "species"))

# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]], 
  hab_press = habitat_pressure, 
  sync = com_data[["sync"]],
  nmds = nmds,
  basin = st_basin 
  )

# Compute SEMs
sem <- compute_stab_sem(.data = sem_data,
  random_effect = as.formula("~1|basin"))

```{r}
ggpiecewisesem(sem)
```

@@

```{r sensitivity, eval = FALSE}
myload(op_analysis, op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))

sem_l_data <- map(list(full = op_analysis, wo_holes = op_analysis_wo_holes, ov = op_analysis_ov),
  ~build_dataset_get_sem_coefficient(
    .op = .x,
    dest_dir = mypath("data", "species"))
)

sem_results <- map(sem_l_data,
  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
  enframe() %>%
  rename(dataset = name) %>%
  unnest(value)

# Reformat
colnames(sem_results) <- str_to_lower(colnames(sem_results))
sem_results %>%
  mutate(r_p = str_c(response, predictor, sep = "~")) %>%
  ggplot(aes(x = r_p, y = std.estimate)) +
  geom_point(aes(color = dataset)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
